\subsection{The Reliability Index}
\label{sec:beta}
The reliability index is a unitless constant that can be used to infer the probability of a system or component to fail in service. Roughly, the Reliability index describes the safety factor of a system as the Z-score of a standard normal distribution, where higher numbers indicate higher probabilities of success. It is derived from the basic concept of probability of failure. 

Consider the following definition for the margin of safety for a system under stress \cite{struct-rel}:

\begin{equation}
Z = S_y - \sigma
\end{equation}
where:
\begin{align*}
S_y &= \text{Material Yielding Stress}\\
\sigma &= \text{Von Mises Stress resulting from the applied Load}
\end{align*}
If ``failure" is defined as \cite{struct-rel}:

\begin{align}
G\left( S_y, \sigma\right) &= S_y - \sigma \le 0\nonumber\\
G\left( S_y, \sigma\right) &= Z < 0
\end{align}
If we treat $Z$ as a random variable with a Gaussian distribution, The probability of failure occurring ($P_f$) is given as \cite{struct-rel}:

\begin{align}
P_f = P(Z<0) &= \Phi \left( \frac{0 - \mu_Z}{\sigma_Z}  \right)\nonumber\\
P_f &= 1 - \Phi \left( \frac{\mu_Z}{\sigma_Z} \right)\nonumber\\
P_f &= 1 - \Phi \left( \beta \right)\label{eq:Pf}
\end{align}
where:
\begin{align*}
\mu_Z &= \text{Mean of Z}\\
\sigma_Z &= \text{Standard Deviation of Z}\\
\Phi(x) &= \text{The CDF of the Normal (Gaussian) Distribution}
\end{align*}
From the above, it is clear we have defined $\beta$ as:

\begin{equation}
\beta = \frac{\mu_Z}{\sigma_z}\label{eq:protobeta}
\end{equation}
For the random variable $Z$, the mean and standard deviation are \cite{risk2}:
\begin{align}
\mu_Z &= \mu_{Sy} - \mu_\sigma\label{eq:muZ}\\
\sigma_Z &= \sqrt{\sigma_{\sigma}^2 + \sigma_{Sy}^2}\label{eq:sigmaZ}
\end{align}
where
   \begin{align*}
	   \mu_{Sy} &= \text{Mean of} S_y\\
	   \sigma_{Sy} &= \text{Std. Deviation of }S_y\\
	   \mu_{\sigma} &= \text{Mean of }\sigma\\
	   \sigma_{\sigma} &= \text{Std. Deviation of }\sigma
   \end{align*}
Substituting Equations \ref{eq:muZ} and \ref{eq:sigmaZ} into Equation \ref{eq:protobeta} yields:
   \begin{equation}
	   \beta = \frac{\mu_{Sy} - \mu_\sigma}{\sqrt{\sigma_{\sigma}^2 + \sigma_{Sy}^2}}
	   \label{eq:beta}
   \end{equation}

Equation \ref{eq:beta} represents the Reliability Index. This is the primary metric used to measure reliability in the Stochastic Loads method presented here. If we define reliability as \cite{risk2}: 

\begin{equation}
R = 1 - P_f
\end{equation}
The relation between $\beta$ and Reliability is clearly given from Equation \ref{eq:Pf}:
\begin{align}
R &= 1 - \left(1 - \Phi (\beta)\right)\nonumber\\
&= \Phi(\beta)
\end{align}
For example, for a value of $\beta$ of 1.96, the reliability is calculated as 97.5\%. For a $\beta$ value of 2.58, reliability rises to 99.5\%. 

In order to evaluate $\beta$ for the designs presented in this study, Equation \ref{eq:beta} will be used. To satisfy all the variables in this equation, the mean and standard deviation for both the material yield criterion and the applied Von Mises stress must be found. The properties related to properties of the material the object is made from are given assumed values that will be held constant across all designs. The stress-related properties, however, must be calculated.

\subsubsection{Finding $\mu_\sigma$ and $\sigma_\sigma$}
If $g(x_1, x_2, ... x_n) = Y$ denotes a function of multiple random variates and a single, dependent variable, let:\todo{cite} 
   \begin{align}
	   \mu(Y) = g(x_1, x_2, ... x_n) + \frac{1}{2} \sum_{i=1}^{n}\left( \frac{\partial^2 g}{\partial x_i^2} \sigma_{xi}^2  \right)
	            \label{eq:mu}\\
	   \sigma^2(Y) = \sum_{i=1}^{n}\left( \frac{\partial g}{\partial x_i} \sigma_{xi}  \right)^2 + 
			 \frac{1}{4} \sum_{i=1}^{n}\left( \frac{\partial^2 g}{\partial x_i^2} \sigma_{xi}^2  \right)^2 \label{eq:sigma}
   \end{align}
In our case, the term $Y$ will be the Von Mises Stress of our beam system. The tensor definition of the Von Mises stress at a given location can be written as:
   \begin{equation}
      \sigma = \sqrt{\frac{3}{2} \cdot \left(\sigma_{dev}:\sigma_{dev} \right)}
	\label{eq:basedef}
   \end{equation}
Where $\sigma_{dev}$ is the stress deviator tensor, which will be more completely addressed later. 
We can simplify derivation of equation \ref{eq:basedef} by hiding the tensor contraction in the equation with a placeholder variable:
   \begin{align}
	   \alpha = (\sigma_{dev}:\sigma_{dev})
	   \label{eq:defalpha}
   \end{align}
This turns equation \ref{eq:basedef} into:
   \begin{align}
      \sigma' = \sqrt{\frac{3}{2} \cdot \left(\alpha\right)}
   \end{align}
This simplified equation can be derived as shown below: 
   \begin{align}
	   \frac{\partial \sigma'}{\partial P_x} &= \sqrt{\frac{3}{2}} \left[\frac{1}{2} \frac{\partial \alpha}{\partial P_x} 
						    \left( \alpha \right)^{-\frac{1}{2}}\right]\label{eq:fd_vmx}\\
	   \frac{\partial^2 \sigma'}{\partial P_x^2} &= \sqrt{\frac{3}{2}} \left[ \frac{1}{2}  \frac{\partial ^2 \alpha}{\partial P_x^2}
	                                                \left( \alpha \right)^{-\frac{1}{2}} - 
							\frac{1}{4}  
							\left(\frac{\partial \alpha}{\partial P_x}\right)^2
							\left( \alpha \right)^{-\frac{3}{2}}\right] \\
	   \frac{\partial \sigma'}{\partial P_y} &= \sqrt{\frac{3}{2}} \left[\frac{1}{2} \frac{\partial \alpha}{\partial P_y} 
						    \left( \alpha \right)^{-\frac{1}{2}}\right]\\
	   \frac{\partial^2 \sigma'}{\partial P_y^2} &= \sqrt{\frac{3}{2}} \left[ \frac{1}{2}  \frac{\partial ^2 \alpha}{\partial P_y^2}
	                                                \left( \alpha \right)^{-\frac{1}{2}} - 
							\frac{1}{4}   
							\left(\frac{\partial \alpha}{\partial P_y}\right)^2
							\left( \alpha \right)^{-\frac{3}{2}}\right] \label{eq:sd_vmy}
   \end{align}
Of course, this introduces derivatives of $\alpha$ as values that must be calculated. In order to calculate these derivatives, the concept and application of the deviator tensor must be investigated further.


The Deviatoric Stress Tensor (or deviator tensor) describes the component of stress that tends to deform an element. It is given in terms of the overall stress tensor $\sigma'$ as: 
   \begin{equation}
      \sigma_{dev} = \sigma' - \frac{1}{3} \mathrm{tr}(\sigma') \left[ \mathbf{I} \right]
   \end{equation}
For purposes that will become clear later, we can call this operation a matrix operator $\gamma$:
   \begin{align}
      \gamma(x) &= x - \frac{1}{3} \mathrm{tr}(x) \left[ \mathbf{I} \right]\label{eq:gamma}\\
      \sigma_{dev} &= \gamma(\sigma') \nonumber
   \end{align}
In this study, $\sigma'$ is constructed from the component response tensors, $\sigma_{Px}$ and $\sigma_{Py}$. These are tensors that correspond to the stresses in the material when a unit load is applied in the x- and y- directions, respectively. These tensors can be used to define $\sigma'$:
   \begin{equation*}
      \sigma' = \sigma_{Px} \cdot P_x + \sigma_{Py} \cdot P_y
   \end{equation*}
Applying equation \ref{eq:gamma} to the above definition of $\sigma'$ yields:
   \begin{align}
	   \gamma_(\sigma') &= \left(\sigma_{Px} \cdot P_x + \sigma_{Py} \cdot P_y\right) - 
                       \frac{1}{3} \mathrm{tr} \left(\sigma_{Px} \cdot P_x + \sigma_{Py}
                       \cdot P_y\right) \left[ \mathbf{I} \right] 
   \end{align}
From here, it is important to remember that taking the trace of a matrix is a distributive operation, as is multiplying a scalar and a matrix. Therefore, the above equation can be rewritten as: 
   \begin{align}
	   \gamma(\sigma') &= \left(\sigma_{Px} \cdot P_x + \sigma_{Py} \cdot P_y\right) - 
                       \frac{1}{3} \left(\mathrm{tr} \left(\sigma_{Px} \cdot P_x\right) +
                       \mathrm{tr} \left( \sigma_{Py} \cdot P_y\right)\right) 
                       \left[ \mathbf{I} \right]\nonumber \\
                      &= \left(\sigma_{Px} \cdot P_x + \sigma_{Py} \cdot P_y\right) - 
		       \frac{1}{3} \left(\mathrm{tr} \left(\sigma_{Px} \cdot P_x\right)
		       \left[ \mathbf{I} \right] +
                       \mathrm{tr} \left( \sigma_{Py} \cdot P_y\right) 
                       \left[ \mathbf{I} \right]\right)\nonumber\\
		      &= \left(\sigma_{Px} \cdot P_x + \sigma_{Py} \cdot P_y\right) - 
		       \frac{1}{3} \left(P_x \cdot \mathrm{tr} \left(\sigma_{Px}\right)
		       \left[ \mathbf{I} \right] +
                       P_y \cdot \mathrm{tr} \left( \sigma_{Py} \right) 
                       \left[ \mathbf{I} \right]\right)\nonumber\\
		      &= P_x \cdot \left( \sigma_{Px} - \frac{1}{3} \mathrm{tr}(\sigma_{Px})
			 \left[ \mathbf{I} \right] \right) + P_y \cdot \left( \sigma_{Py} -
			 \frac{1}{3} \mathrm{tr}(\sigma_{Py})
			 \left[ \mathbf{I} \right] \right)\nonumber\\
		      &= P_x \cdot \gamma(\sigma_{Px}) + P_y \cdot \gamma(\sigma_{Py})
   \end{align}
Note that the terms $\gamma(\sigma_{Px})$ and $\gamma(\sigma_{Py})$ do not contain any terms related to $P_x$ or $P_y$. This implies that they are constant when deriving with respect to these variables. From this point forward, we will refer to these deviatoric unit tensors as:

   \begin{align*}
	   \gamma(\sigma_{Px}) &= \sigma_{devx}\\
	   \gamma(\sigma_{Py}) &= \sigma_{devy}
   \end{align*}
This means: 
   \begin{equation}
	   \sigma_{dev} = \sigma_{devx} \cdot P_x + \sigma_{devy} \cdot P_y
   \end{equation}

Returning to equation \ref{eq:defalpha}, we can begin to define $\alpha$ in terms of these new tensors. To start with, we need to breakdown the ``:" operator in the equation. This is the tensor contraction operator, and is defined as: 
   \begin{equation}
	   \left[A\right] : \left[B\right] = \mathrm{tr}(\left[A\right]\left[B\right])
	   \label{eq:tensorcont}
   \end{equation}
Because both matrix multiplication and the trace of a matrix are both distributive, the tensor contraction operator is also distributive. Using the definition in \ref{eq:tensorcont} and applying it to \ref{eq:defalpha} yields: 
   \begin{align}
	   \alpha &= \mathrm{tr}\left[(\sigma_{devx} \cdot P_x + \sigma_{devy} \cdot P_y) \cdot
		    (\sigma_{devx} \cdot P_x + \sigma_{devy} \cdot P_y)\right]\nonumber\\
		  &= \mathrm{tr}\left[\sigma_{devx} \cdot \sigma_{devx} \cdot P_x^2 + \left( 
		     \sigma_{devx} \cdot \sigma_{devy} + \sigma_{devy} \cdot \sigma_{devx} \right) \cdot P_x P_y + 
		     \sigma_{devy} \cdot \sigma_{devy} \cdot P_y^2 \right]\\
		  &= \mathrm{tr}\left[ \sigma_{devx} \cdot \sigma_{devx} \right] \cdot P_x^2 +  
		     \mathrm{tr}\left[ \sigma_{devx} \cdot \sigma_{devy} + \sigma_{devy} \cdot \sigma_{devx} \right]
                     \cdot P_x P_y + \mathrm{tr}\left[ \sigma_{devy} \cdot \sigma_{devy}\right] \cdot P_y^2
   \end{align}
Note that the center term is arranged as shown due to the non-commutative nature of matrix multiplication.
Now, we can take this definition of $\alpha$ and easily find the derivatives we need.
   \begin{align}
	   \frac{\partial \alpha}{\partial P_x} &= 
	   	\mathrm{tr}\left[\sigma_{devx} \cdot \sigma_{devx}\right] \cdot 2P_x + \mathrm{tr} \left[ 
		     \sigma_{devx} \cdot \sigma_{devy} + \sigma_{devy} \cdot \sigma_{devx} \right] \cdot P_y\label{eq:fd_ax}\\
	   \frac{\partial^2 \alpha}{\partial P_x^2} &=
	   	\mathrm{tr}\left[ \sigma_{devx} \cdot \sigma_{devx} \right] \cdot 2\\
	   \frac{\partial \alpha}{\partial P_y} &= 
	   	\mathrm{tr}\left[\sigma_{devy} \cdot \sigma_{devy}\right] \cdot 2P_y + \mathrm{tr} \left[ 
		     \sigma_{devx} \cdot \sigma_{devy} + \sigma_{devy} \cdot \sigma_{devx} \right] \cdot P_x\\
	   \frac{\partial^2 \alpha}{\partial P_x^2} &=
		\mathrm{tr}\left[\sigma_{devy} \cdot \sigma_{devy} \right]\cdot 2\label{eq:sd_ay}
   \end{align}

   With equations \ref{eq:fd_ax} through \ref{eq:sd_ay} coupled with equations \ref{eq:fd_vmx} through \ref{eq:sd_vmy}, we have all of the terms needed to construct and solve equations \ref{eq:mu} and \ref{eq:sigma}, substituting the equation for $\sigma$ into $Y$ for both equations. It is then easy to substitute the results of equations \ref{eq:mu} and \ref{eq:sigma} into \ref{eq:beta} and determine $\beta$.  In the code presented with this report, all of these terms are assembled separately and combined. Therefore, the final equation with all substitutions performed will not be shown here.

\subsubsection{Validating the derivation for $\mu_\sigma$ and $\sigma_\sigma$}
The equations for finding $\mu_\sigma$ and $\sigma_\sigma$ were validated by comparing the results from the equation to a Monte Carlo Simulation of the equation system. One of the test systems used was the following states of stress:

The mean and standard deviation of the input loads to the material was assumed to be:
\begin{align*}
    \mu_{px} &= 25 &\sigma_{px} &= 3.25\\
    \mu_{py} &= 150 &\sigma_{py} &= 19.5\\
\end{align*}

The unit response to stress was assumed to be: 
\begin{align*}
    U_{xpx} &= 2500  &U_{ypx} &= 750  &U_{xypx} &= 320\\
    U_{xpy} &= 250  &U_{ypy} &= 7500  &U_{xypy} &= 210
\end{align*}

The above unit responses can be represented as tensors. These tensors are: 

\begin{align*}
\mathbf{U}_{px} &= \left[ 
\begin{matrix}
2500 & 320 & 0\\
320 & 750 & 0\\
0 & 0 & 0
\end{matrix}
\right]
&\mathbf{U}_{py} &= \left[
\begin{matrix}
250&210&0\\
210&7500&0\\
0&0&0
\end{matrix}
\right]
\end{align*}

The deviators of these tensors are: 

\begin{align*}
\mathbf{\sigma}_{devx} &= \left[ 
\begin{matrix}
1416.67 & 320 & 0\\
320 & -333.3 & 0\\
0 & 0 & -1083.33
\end{matrix}
\right]
&\mathbf{\sigma}_{devy} &= \left[
\begin{matrix}
-2333.3&210&0\\
210&4916.67&0\\
0&0&-2583.33
\end{matrix}
\right]
\end{align*}

A Monte Carlo simulation was prepared using the properties above. A sample size of $1.5\times 10^6$ was used for the simulation. Then, code was created based on the equations \ref{eq:mu} and \ref{eq:sigma}, as well as \ref{eq:fd_ax} to \ref{eq:sd_ay}. This code was run with the same parameters, and results obtained. The results from these two analyses can be seen in Table \ref{tab:val_tensors} below. 

\begin{table}[!hbtp]
\caption{Selected Validation Results for the Taylor Approximation for finding $\mu_\sigma$ and $\sigma_\sigma$}
\small
\label{tab:val_tensors}
\begin{center}
\begin{tabular}{|l|p{2.1cm}|p{2.5cm}|p{2.5cm}|}
\hline
& Monte Carlo Simulation & Taylor Expansion Approximation & Error percentage\\
\hline
Expected Value (Mean) & $1.0993 \times 10^6$ & $1.0994 \times 10^6$ & $-3.9552 \times 10^{-4} \;\%$\\
Standard Deviation & $1.4382 \times 10^5$ & $1.4386 \times 10^5$ & $-3.2071 \times 10^{-2} \;\%$\\
\hline
\end{tabular}
\end{center}
\end{table}

Based on this table, it is plainly apparent that the tensor-based Taylor Series Approximation for finding $\mu_\sigma$ and $\sigma_\sigma$ is an appropriate approximation method. The code that was developed for the validation is identical to the code in the final product in the main analysis loop. 
